\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome5} %This is for icons
\usepackage{mathptmx} %This sets Times as the font


\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    { #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4}
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{--}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\href{https://png270.github.io/}{\Large Siddhi Lad}} \\
  \vspace{1mm}
  \faEnvelope \ \href{mailto:siddhi.lad00@gmail.com}{ siddhi.lad00@gmail.com} \quad | \quad \faLinkedin \href{https://www.linkedin.com/in/siddhi-lad/}{ linkedin.com/in/siddhi-lad/} \quad | \quad \faGithub \href{https://github.com/png270}{ github.com/png270}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Pennsylvania State University}{State College, PA}
      {Master of Science in Cybersecurity Analytics \& Operations; GPA: 4.00}{Aug 2024 -- May 2026}
      \vspace{2mm} \\
      { \textbf{Relevant Coursework} - Computer Security, Threat Hunting and Offensive Security, Cyber Physical Systems and IoT Security, Network Management}     
    \resumeSubheading
      {NIIT University}{Rajasthan, India}
      {Bachelor of Technology in Computer Science \& Engineering; GPA: 3.21 (8.03/10.0)}{Aug 2018 -- July 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BSM India Pvt. Ltd.}{Mumbai, India}
      {Cybersecurity Intern}{Jun 2025 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{}
          {Built an internal tool that reduces the time to detect changes in firewall configuration by 50\%, using Regex, Pandas and Streamlit to automate the parsing and comparison of XML files.}
        \resumeItem{}
          {Engineered a proof-of-concept for remote device management on maritime vessels, utilizing Ansible and PowerShell to ensure the continuity and security of critical systems in low-connectivity environments.}
          \resumeItem{}
          {Proposed improvements over currently implemented incident response strategies to facilitate seamless coordination between vendors and IT teams.}
          \resumeItem{}
          {Performed host-based forensic analysis and triage to identify IOCs and scope malware infection.}
      \resumeItemListEnd
      
%-------------------------------------------

    \resumeSubheading
      {IBM India Pvt. Ltd.}{Bangalore, India}
      {Information Security Analyst}{Sept 2022 -- May 2024}
      \resumeItemListStart
        \resumeItem{}
          {Configured, tuned, and monitored Imperva Cloud WAF for a major healthcare client, ensuring continuous web application security and compliance.}
        \resumeItem{}
          {Implemented custom security rules across 1,000+ healthcare web applications, mitigating threats such as SQLi, XSS, and DDOS/DOS attacks.}
        \resumeItem{}
          {Contributed to incident response efforts by rapidly troubleshooting and resolving WAF issues, helping to contain security incidents and restore normal operations.}
        \resumeItem{}
          {Documented and tracked infrastructure changes in ServiceNow, collaborated with development teams to integrate WAF security policies, and worked with vendors to troubleshoot and resolve recurring WAF issues.}
      \resumeItemListEnd

      % --------Multiple Positions Heading------------
    \resumeSubSubheading
     {Information Security Analyst Intern}{Jan 2022 - Jun 2022}
     \resumeItemListStart
        \resumeItem{}
          {Developed Python automation scripts to streamline pre- and post-upgrade quality checks for Cisco ASA Firewalls, reducing manual efforts by 60\%.}
        \resumeItem{}
          {Established secure SSH sessions with Paramiko and implemented Regex-based log parsing to verify firewall configurations before and after upgrades thereby reducing errors and ensuring reliable deployments.}
     \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{}{
  \textbf{Programming} - Python, C/C++, Go, PowerShell, Bash
  }
    \resumeSubItem{}{
  \textbf{Web Development} - HTML, CSS, Node.js, JavaScript, Django, Streamlit
  }
    \resumeSubItem{}{
  \textbf{Dev-Ops \& Security} - AWS (EC2, VPC, S3), Docker, Ansible, Git, Imperva Cloud WAF, Cisco ASA, Nmap, Wireshark
  }
    \resumeSubItem{}{
  \textbf{OS} - Linux (Ubuntu, Kali), Windows
  }
    \resumeSubItem{}{
  \textbf{Core Competencies} - MITRE ATT\&CK, Threat Modeling, Incident Response, Network Security, Compliance \& Governance
  }
  
  \resumeSubHeadingListEnd

%------CERTIFICATIONS--------
\section{Certifications}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l@{\extracolsep{\fill}}l}
  {Certified Ethical Hacker (CEH v11)} & {CompTIA Security+} & {AWS Certified Cloud Practitioner}
\end{tabular*}

%-----------EXTRAS-----------------
\section{Competitions and Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{}
      {Placed 313/950 teams in CTF@CIT by solving challenges in OSINT, Crypto, and Steganography.}
    \resumeSubItem{}
      {Competed in National Centers of Academic Excellence in Cybersecurity (NCAE-C); collaborated with a team to defend infrastructure and solve complex CTF challenges.}
    \resumeSubItem{}
      {Secured first place at the Smart India Hackathon (SIH) 2020; worked on a mobile and web application that helps farmers and the government manage crops efficiently and compensate for losses.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

